A graph-based data model for interactive evolutionary computation

### 2017-01-17 2017-CEC-Graph-Based-Population-For- IEC/paper.tex
A bit of revision
But more grammar revision and adding the rest of the paper is needed

\section{Introduction}
Interactive Evolutionary Algorithms (IEAs): are standard EAs whose
fitness evaluations are performed by persons with in an interactive 
system.  Thus, the main loop of the EA needs the intervention of a
human for the quality assessment of each proposed solution. These
systems have an inherent drawback araising from the very nature of 
the algorithm, namely, the human fatigue caused by the interaction. 
Some authors have already tried to address this basic problem \cite{Frade:2010:EvoGAMES}.
nevertheless, IEAs have demonstrated their ability for effectively
producing art and design \cite{Bentley:1999:intro,Sims:1991,todd:1992},
as well as other products in many other domains \cite{ie1}. 
Several IEC have been developed as web based systems \cite{picbreeder},
who depend on volunteers who visit the system to interactively help
with the search, using both anonymous and registered users. In particular
the EvoSpace-Interactive (ES-I) platform employs a collaborative technique,
where several registered users assign a quality assessment to a single
individual and then an aggregated fitness value is calculated. The fitness
assigned to each individual depends on the taste of each particular user, 
resulting in a many-to-many relationship between users and individuals. 
Many systems query this user-individual relation to extract relevant
knowledge about the process and the population, for instance showing the
most popular individual, or the the user with more participation \cite{picbreeder}.
In order to do this, individuals about individuals must be stored, even
if they are no longer in the active population. In this work a graph database
is proposed to model the interaction between users and individuals, with
the following advantages:

@@

The remainder of this paper proceeds as follows.
Section \ref{sec:interactive} presents related work on the topic 
of Interactive Evolution data models.
Then, Section \ref{sec:evospace-i} presents the computational platform on which the main proposal of this work is developed. The proposed graph model is presented in Section \ref{sec:graph}.
The experimental work and results are presented in Section \ref{sec:experiments}.
Finally, a concluding remarks are provided in Section \ref{sec:conclusions}.

@@

Users are a central part of an IEC system, because not only their
explicit evaluation is involved, the overall context of interaction
affects the system as a whole as users interact not only with the graphical
interface, and each individual\'s phenotype, there is also the interaction
with other users, their previous evaluations and their own history of activities
and past experiences. Thus users in this proposal are dinamic entities 
interacting with an evolutionary computation and
have the fundamental purpose of evaluating individuals according to their preferences,
both explicitly or implicitly. Their degree of participation is affected by 
the context of use. With the porpouse of modeling the system, the contextual
factors are abstracted using a graph. This graph can then be used to 
enhance the system to capture the attention of users and possibly
increase their participation and mitigate the fatige.

The current model is tailored to the EvoSpace-I functionality and capabilities
but it can be modified to handle other platforms.

@@

Currently there exist some basic actions that
users can perform in the system, in order to interact with EvoSpace-I platform
users must login to the system through their facebook account. 
Once a user has logged-in to the system, he or she can do several actions.
Example of actions are the following:

@@

Another example is the sharing action, that can occur when In this sense the action of posting is when
users want to put something on their wall who want others to know through
their social networks. Likewise the storing action occurs when users want to
retain permanently information that are of their interest. Finally the
browsing action occurs when users are exploring content for their needs. All
these actions go beyond only evaluating individuals.

@@

In figure \ref{fig:User_node} the vertex $u$ properties are shown.

@@

The “id” property defines that the vertex $i$ has a unique identifier in the set
of vertices, which means that there will not be duplicate vertices. The
“chromosome” property defines the chromosome of the individual representing the
vertex $i$. which as defined above in this section. The  property “views” defines
the amount that users have seen this vertex $i$ The property “element\_type”
defines the element type that will be the vertex $i$. The property “created”
defines the creation date of the vertex $i$.

@@

Already defined the vertices and edges a graph-based user-individual model is
proposed where vertices users are related to the vertices individuals, likewise
the vertices individuals are related to themselves when evolution exist between
them. In that sense the vertices users and individuals are related to the
vertices collections as a vertex user can be related to a vertex collections and
a vertex collections collections is related to $n$ individuals vertex. In Figure
\ref{fig:user_moder} shows an example of the graph-based user-individual model.

>>>>

\section{Introduction}
% Maybe an introduction on why and where to use these types of
% algorithms? - jj
Interactive Evolutionary Algorithms (IEAs) are standard EAs whose
fitness evaluations are performed by persons within an interactive 
system.  Thus, the main loop of the EA needs the intervention of a
human for the quality assessment of each proposed solution. These
systems have an inherent drawback arising from the very nature of 
the algorithm, namely, the human fatigue caused by the interaction. % Can it be quantified? Maybe a reference to NodIO? - JJ
Some authors have already tried to address this basic problem
\cite{Frade:2010:EvoGAMES}. %Non sequitur. Is it something we are
                            %going to do here? - jj

% Maybe this claim should go to the beginning. THIS is why we want to
% use them - JJ
Nevertheless, IEAs have demonstrated their ability for effectively
producing art and design \cite{Bentley:1999:intro,Sims:1991,todd:1992},
as well as other products in many other domains \cite{ie1}. 
Several IECs have been developed as web based systems \cite{picbreeder},
who depend on volunteers who visit the system to interactively help
with the search, using both anonymous and registered users. In particular
the EvoSpace-Interactive (ES-I) %citation
platform employs a collaborative technique,
where several registered users assign a quality assessment to a single
individual and then an aggregated fitness value is calculated. The fitness
assigned to each individual depends on the taste of each particular user, 
resulting in a many-to-many relationship between users and individuals. 
Many systems query this user-individual relation to extract relevant
knowledge about the process and the population, for instance showing the
most popular individual, or the the user with more participation \cite{picbreeder}.
In order to do this, individuals about individuals %what? Maybe data
                                %about individuals? - JJ
must be stored, even
if they are no longer in the active population. In this work a graph database
is proposed to model the interaction between users and individuals, with
the following advantages:

@@

The remainder of this paper is organized  as follows.
Section \ref{sec:interactive} presents related work on the topic 
of Interactive Evolution data models.
Then, Section \ref{sec:evospace-i} presents the computational platform on which the main proposal of this work is developed. The proposed graph model is presented in Section \ref{sec:graph}.
The experimental work and results are presented in Section \ref{sec:experiments}.
Finally, a concluding remarks are provided in Section \ref{sec:conclusions}.

@@

Users are a central part of an IEC system,  not only because their
explicit evaluation is essential, but also because the overall context of interaction
affects the system as a whole as users interact not only with the graphical
interface, and each individual\'s phenotype, there is also the interaction
with other users, their previous evaluations and their own history of activities
and past experiences. Thus users in this proposal are dinamic entities 
interacting with an evolutionary computation and
have the fundamental purpose of evaluating individuals according to their preferences,
both explicitly or implicitly. Their degree of participation is affected by 
the context of use. With the porpouse of modeling the system, the contextual
factors are abstracted using a graph. This graph can then be used to 
enhance the system to capture the attention of users and possibly
increase their participation and mitigate the fatige.

The current model is tailored to the EvoSpace-I functionality and capabilities
but it can be modified to handle other platforms. %A hint on how

@@

Currently there are some basic actions that
users can perform in the system, in order to interact with EvoSpace-I platform
users must login to the system through their facebook account. 
Once a user has logged-in to the system, he or she can do several actions.
Example of actions are the following:

@@

Another example is the sharing action, that can occur when %Something
% missing here - JJ

In this sense the action of posting is when
users want to put something on their wall who want others to know through
their social networks. Likewise the storing action occurs when users want to
retain permanently information that are of their interest. Finally the
browsing action occurs when users are exploring content for their needs. All
these actions go beyond only evaluating individuals.

@@

In figure \ref{fig:User_node} the properties of vertex $u$  are shown.

@@

The “id” property defines that the vertex $i$ has a unique identifier in the set
of vertices, which means that there will not be duplicate vertices. The
“chromosome” property defines the chromosome of the individual representing the
vertex $i$. which as defined above in this section. The  property “views” defines
the amount that users have seen this vertex $i$ The property “element\_type”
defines the element type that will be the vertex $i$. The property “created”
defines the creation date of the vertex $i$. % Is there a point in
                                % describing these properties? - JJ

@@

Once  the vertices and edges have been defined a graph-based user-individual model is
proposed where  user vertices are related to the individual vertices, likewise
the vertices individuals are related to themselves when evolution exist between
them. % Grammar has to be improved - JJ
In that sense the vertices users and individuals are related to the
vertices collections as a vertex user can be related to a vertex collections and
a vertex collections collections is related to $n$ individuals vertex. In Figure
\ref{fig:user_moder} shows an example of the graph-based user-individual model.
